\documentclass[11pt]{article}
%\usepackage[margin=1in]{geometry} % Makes margins be 1 inch
\usepackage[bottom=0.4in,top=.6in, left = .8in, right = .6in]{geometry}
\usepackage{helvet} % Sets font to Helvetica
\renewcommand{\familydefault}{\sfdefault} % Sets default font to Sans Serif
\setcounter{secnumdepth}{0} % Removes numbering for sections and subsections
\pagenumbering{gobble} % Removes page numbering from bottom
\usepackage{multirow}% http://ctan.org/pkg/multirow
\usepackage{fontspec}
\usepackage{fontawesome} % enables use of Icons
\usepackage{titlesec}
\usepackage{enumitem}
\setlist{nosep} % removes vertical spacing for list items
\usepackage{float} % here for H placement parameter
\usepackage{hyperref}
\usepackage{lipsum}
% Section below removes line spacing below Section, Subsection and Subsubsection headings
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

\begin{document}
	\def\arraystretch{1.3}	 % affects padding of table
%	\begin{table}
%	\begin{tabular}{|c|c|c|}
%	\multicolumn{3}{l}{\Huge \noindent David \textbf{McInerney} CV} \\	
%	\hline
%	{\Large \faEnvelopeO}  David.McI.525@gmail.com & {\Large \faPhone}  437-333-2961 &  {\Large \faLinkedin}   \href{http://www.linkedin.com/in/davidbmcinerney}{/davidbmcinerney} \\ 
%	\hline
%	\end{tabular}
%	\end{table}	
	\hspace*{-\parindent} % Removes left intent from minipage	
	\begin{minipage}[b]{0.68\textwidth}
	\begin{flushleft}
	{\noindent \Huge David \textbf{McInerney} CV}
	\end{flushleft}	 
	\end{minipage}
	\begin{minipage}[b]{0.32\textwidth}
	\begin{itemize}
		\item[{\Large \faEnvelopeO}] David.McI.525@gmail.com
		\item[{\Large \faPhone}] 437-333-2961
    	\item[{\Large \faLinkedin}]   \href{http://www.linkedin.com/in/davidbmcinerney}{/davidbmcinerney}
	\end{itemize}

	\end{minipage}
	
	
	
	
	
	\section{Education}
		\hrule \hfill % adds horizontal line with minimal spacing
		\subsection{Carleton University (2015 - Present)}
		\noindent Sustainable and Renewable Energy Engineering (Electrical Stream), Faculty of Engineering 
	
	\section{Work Experience}
		\hrule \hfill % adds horizontal line with minimal spacing
		\subsection{Summer Student at The Siroky Group (Toronto, May 2018 - July 2018)}
		\noindent The Siroky Group provides software solutions to the outdoor advertising industry. The software products usually help with things like managing advertisements on billboards and public transit. While employed as a summer student, I did the following:
		\begin{itemize}
		\item Wrote a program to collect business data (e.g., name, location, and details of businesses) to use in product demos. My Python program extracted data about thousands of business locations using the Google Maps API, formatted them into demo data and incorporated the data into the software. 
		\item A website was being set up for a prospective client, and content was needed. All of the photosheets of the billboards from the client's existing website needed to be downloaded and identified by the board number and description contained in the photo. My Python program found and downloaded all the photos on the site, used OCR to identify the panel number and description in the photo, then added the data into a database. 
		\item Executed test scripts on web and mobile applications. Reported bugs to developers and identified errors in the test scripts.
		\end{itemize}
		\subsection{Janitor at Eurest Services (Ottawa, July 2017 - April 2018)}
		\noindent Cleaning stands, washrooms and general area and restocking washrooms.
		\subsection{Programming Intern at Mocato (Toronto, May 2016 - August 2016)}
%		\begin{itemize}
%		\item Worked closely with project lead to establish and clarify functional and non-functional requirements for application.
%        \item Participated in regular team meetings to receive feedback, provide the status on iterative improvements to the application and strategize forthcoming development activities.
%        \item Ensured application would store and filter client data for client record management as per end user feedback.
%        \item Developed and implemented application testing plan based on scenarios described by project lead.
%        \item Developed this application over two months (under minimal supervision) using C\#, Microsoft Access and Visual Studio.
%		\end{itemize}
		
		\noindent Wrote an application used for business transaction processing. The application takes information about clients and transactions to generate Electronic Fund Transfer (EFT) files. I developed this application (with minimal supervision) using C\# and Microsoft Access.
		
	
	
	\section{\textless Skills/\textgreater}
	\hrule \hfill % adds horizontal line with minimal spacing	

	\noindent \textbf{Intermediate: } Python, HTML, CSS, \LaTeX
	\\
	\noindent \textbf{Beginner: } Javascript, Java, \LaTeX , C\#, C++, MATLAB
		
	
	\section{Personal Projects}
	\hrule \hfill % adds horizontal line with minimal spacing
	\subsection{Javascript Super Mario Game}	
	\noindent Wrote Super Mario-like game in Javascript. You can see it at \href{http://davidmci.ca/italianPlumberSibs}{davidmci.ca/italianPlumberSibs}

	
	\section{Volunteer Experience \& Extracurricular Activities}
	\hrule \hfill
	\iffalse	
	\subsection{Director of Silly Walks at Student Energy Carleton (Ottawa, Jan 2019 - Present)}
	
	\noindent Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero, pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum,erat ligula aliquet magna, vitae ornare odio metus a mi. % Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.
	
	\fi
	
	\subsection{Team Volunteer at Student Energy Carleton (Ottawa, Feb 2018 - Present)}
\noindent I attended team meetings to plan and organize events to encourage and facilitate student engagement with sustainable energy. One highlight was putting on “Women in Energy”, a panel discussion and networking event highlighting and celebrating women’s contributions to the energy sector.
	
\end{document}
